---
title: "Custom conditions"
author: "Kirill Müller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

> R doesn’t come with a built-in constructor function for conditions, but we can easily add one.
>
> (Advanced R, by Hadley Wickham)

Actually, there is `simpleCondition()`, `simpleError()` and the like,
but they don't allow specifying an additional class.
The functions in this package allow it:

```{r}
library(condition)
cond <- new_error("Something went wrong", class = "oops")
cond
is.error(cond)
```

Everything is powered by an R6 generator class that creates condition class
objects:

```{r}
Condition
Error
```

These condition objects can be used instead the plain functions:

```{r}
Error$new("Plain error")
```

If a custom condition is used more than once, it is a good idea to formalize it:

```{r}
Oops <- ConditionClass$new("oops", Error)
oops <- Oops$new("Something went wrong")
oops
Oops$is(oops)
```
